On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-09-07 MS.tex
FigS9 updated FigS4 Graph with and without distinction of relative and absolute growth rate are merged

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4b.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage. Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Results shown here are from the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
\label{fig:figA4}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions). The colours correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
\label{fig:figA8}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart. The mean coefficients are weighted by sample size and established from 112 articles and. Results shown here are from the ''ideal dataset''.  ''n'' indicate the number of correlation.}
\label{fig:figA4}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} Results shown here are from the ``complete'' dataset (recorded under both unstressed and stressed conditions). On the right side of each graph are the Absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).}
\label{fig:figA8}
\end{figure}
